Compiling refinement types to dependent types

### 2020-07-10 tex/paper.tex
Add \tranctx, \tranty, \tranterm commands for consistency

@@

We start with defining $\mu_\Gamma$,
which merely translates the types of the bindings in the context from the surface language into the core language:
\begin{equation}
\begin{aligned}
  & \mu_\Gamma(\emptyset)                                       && \triangleq \emptyset                                                     \\
  & \mu_\Gamma(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \mu_\Gamma(\nonterm G), \gterm x : \mu_\tau(\nonterm{ts})     \\
\end{aligned}
\end{equation}

$\mu_\tau$ is defined as follows,
with the slight abuse of notation to allow ``recursive'' calls
on refinement part of the surface language syntax:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)              \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}              \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))                      \\
  & \mu_\tau( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \mu_\varepsilon(\nonterm{es}_1) \equiv \mu_\varepsilon(\nonterm{es}_2)  \\
  & \mu_\tau(B)                                                 && \triangleq B                                                                       \\
%TODO this last one is not well-defined
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

>>>>

\newcommand{\tranctx}{\mu_\Gamma}
\newcommand{\tranty}{\mu_\tau}
\newcommand{\tranterm}{\mu_\varepsilon}

@@

We start with defining $\tranctx$,
which merely translates the types of the bindings in the context from the surface language into the core language:
\begin{equation}
\begin{aligned}
  & \tranctx(\emptyset)                                       && \triangleq \emptyset                                               \\
  & \tranctx(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \tranctx(\nonterm G), \gterm x : \tranty(\nonterm{ts})  \\
\end{aligned}
\end{equation}

$\tranty$ is defined as follows,
with the slight abuse of notation to allow ``recursive'' calls
on refinement part of the surface language syntax:
\begin{equation}
\begin{aligned}
  & \tranty( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \tranty(\nonterm{ts}_1). \tranty(\nonterm{ts}_2)     \\
  & \tranty( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \tranty(\nonterm{ts})\ **\ \tranty(\nonterm r) \}     \\
  & \tranty( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \tranty(\nonterm r_1) , \tranty(\nonterm r_2))             \\
  & \tranty( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \tranterm(\nonterm{es}_1) \equiv \tranterm(\nonterm{es}_2)   \\
  & \tranty(B)                                                 && \triangleq B                                                            \\
%TODO this last one is not well-defined
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}
